%!TEX TS-program = xelatex
\documentclass[10pt]{friggeri-cv}

\begin{document}

\header{Shreshtha}{Gupta}
       {Wealth Manager}


% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
    07874915759

    London, United Kingdom

    

\end{aside}

\section{Summary}

 I graduated from Imperial Business School with Masters in Science in Investment and Wealth Management. I have previously worked in MKU and Horiba as finance intern. My core competencies are - 

\begin{itemize} 
	\item Writing technical reports on stock markets and equities 
	\item Analysis of ETFs in Europe and Asia markets. I have worked in HYSE, NSE and NASDAQ. 
\end{itemize} 


\section{Experience}

\begin{entrylist}

  \entry
    {2017 -- 2018}
    {ETFGI}
    {London, United Kingdom}
    {\emph{ Research Assistant }\\  I graduated from Imperial Business School with Masters in Science in Investment and Wealth Management. I have previously worked in MKU and Horiba as finance intern. My core competencies are -   \begin{itemize}  	\item Writing technical reports on stock markets and equities  	\item Analysis of ETFs in Europe and Asia markets. I have worked in HYSE, NSE and NASDAQ.  	\item Bring coffee for Debbie  \end{itemize} }
 
  \entry
    {2014 -- 2015}
    {MKU Pvt. Ltd.}
    {Kanpur, India}
    {\emph{ Finance Intern }\\ \begin{itemize}  	\item  	 I graduated from Imperial Business School with Masters in Science in Investment and Wealth Management. I have previously worked in MKU and Horiba as finance intern. My core competencies are Writing technical reports on stock markets and equitie  	  	\item Analysis of ETFs in Europe and Asia markets. I have worked in HYSE, NSE and NASDAQ.  \end{itemize} }
 
\end{entrylist}

\section{Education}

\begin{entrylist}

  \entry
    {2016 -- 2017}
    {MSc, {\normalfont Finance }}
    {Imperial Business School}
    {GPA: Distinction\\ I graduated from Imperial Business School with Masters in Science in Investment and Wealth Management. I have previously worked in MKU and Horiba as finance intern. My core competencies are -   \begin{itemize}  	\item Writing technical reports on stock markets and equities  	\item Analysis of ETFs in Europe and Asia markets. I have worked in HYSE, NSE and NASDAQ.  \end{itemize} }


  \entry
    {2012 -- 2015}
    {Bachelors of Finance, {\normalfont BFM }}
    {HR College of Commerece}
    {GPA: 6.95\\ I graduated from Imperial Business School with Masters in Science in Investment and Wealth Management. I have previously worked in MKU and Horiba as finance intern. My core competencies are -   \begin{itemize}  	\item Writing technical reports on stock markets and equities  	\item Analysis of ETFs in Europe and Asia markets. I have worked in HYSE, NSE and NASDAQ.  \end{itemize} }


\end{entrylist}


\section{Awards}

\begin{entrylist}

  \entry
    {2014}
    {Company Secratary, \emph{ICSI}}
    {}
    { Completed Company Secretary certificate course from ICSI  }

  \entry
    {2015}
    {Member, \emph{Finance Society}}
    {}
    { Worked for Finance society as a Treasurer and organised events.   \begin{itemize}  	\item Organized college level equity trading competition  	\item Collected funds for society through alumni  \end{itemize} }

\end{entrylist}


\section{Skills}
 \textbf{Analysis } :\textbf{ } DCF and Financial Modelling, Excel programming 
 
  \textbf{Technical } : Python, VBA, Excel, MATLAB 


\section{Languages}
 \textbf{Fluent Proficiency} : Hindi, English 
 
  \textbf{Working Proficiency} : Spanish, French 
 
  \textbf{Limited Proficiency} : Japanese 

\end{document}
